---
title: "Simple regression"
author: "Gabriel R. R."
date: "6/22/2020"
output: html_document
---
## Disclaimer
------------------------------------------------------------
Data is derived from the book
[Discovering Statistics Using R](https://www.amazon.com.br/gp/product/1446200469/ref=as_li_tl?ie=UTF8&camp=1789&creative=9325&creativeASIN=1446200469&linkCode=as2&tag=reisrgabriel-20&linkId=9d95df74e31356334db328743ef8aec5) by Andy Field Jeremy Miles & Zöe Field (2012).
This is a tutorial to remember key concepts and to store code come in handy in the future.


```{r}
# Reading packages
library(car)
library(ggplot2)
library(QuantPsyc)
```


## Problem
------------------------------------------------------------
A record label is trying to sell more albums.
They've been investing money on advertising *hoping* to sell make their sales
number go up. Unfortunately, they haven't been having much success.
To get a better grip of their business, they hire me to analyze some of the
results they've been getting. They provide me this *unusely clean* data:

```{r}
album <- read.csv("https://raw.githubusercontent.com/GabrielReisR/BasicsOf/master/Data%20Files/Album%20Sales%201.csv",
                   sep = ",")
head(album, n = 5)
tail(album, n = 5)
```

There are 200 rows of data in which adverts equals to how much they've spent on
advertising, while sales represent the number of sales made for that particular
albums. *This is transformed, meaning that the value of 1 in sales equals to 1000.*

### Is there a relationship?
------------------------------------------------------------
Let's look at both of these variables together to see if they've been spending
their money right.


```{r}
albumPlot <- ggplot(album, aes(x = adverts, y = sales)) + 
  labs(x = "Money spent on advertising (on $)",
        y = "Sales (in thousands)") +
  geom_point() + 
  geom_smooth(method = "lm", colour = "#06A9CF", se = F, size = 1.3) + 
  theme_minimal()


albumPlot
```
Now this is a fairly interesting but expected relationship. There seems to be a 
positive relationship between the amount of money spent on advertising and sales 
made by the record label. 
However, when we look at it, we see that if nothing is spent on advertising (X = 0),
the amount of sales made seems to be around 130-150 thousands of sales.
*Should they even be spending money on advertising?

### 